PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
set sum score to NA if missigness in phq

prepandemic
```{r gad prepan missingness}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_prepan_raw =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_prepan])
      )
  )

glad.gad.raw.id %>%
  freq(na_per_person_gad_prepan_raw,
       cumul = F)
```

```{r gad prepan sum score if missigng items set to NA}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    gad.sum_score_prepan =
      if_else(condition = na_per_person_phq_prepan_raw > 0,
              true = NA_real_,
              false = gad.sum_score_prepan,
              missing = NA_real_
              )
  )

summary(glad.gad.raw.id$gad.sum_score_prepan_raw)
summary(glad.gad.raw.id$gad.sum_score_prepan)
```

@@

>>>>

prepandemic
```{r gad prepan missingness}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_prepan])
      )
  )

glad.gad.raw.id %>%
  freq(na_per_person_gad_prepan,
       cumul = F)
```

```{r gad prepan sum score if missigng items set to NA}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    gad.sum_score_prepan =
      if_else(condition = na_per_person_gad_prepan > 0,
              true = NA_real_,
              false = gad.sum_score_prepan_raw,
              missing = NA_real_
              )
  )

glad.gad.raw.id %>%
  descr(gad.sum_score_prepan_raw, stats = "common")

glad.gad.raw.id %>%
  descr(gad.sum_score_prepan, stats = "common")
```

@@

all times
```{r phq prepan sum score if missigng items set to NA - all times}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    phq.sum_score_prepan =
      if_else(condition = na_per_person_phq_prepan > 0,
              true = NA_real_,
              false = phq.sum_score_prepan_raw,
              missing = NA_real_
      )
  )

glad.phq.raw.id %>%
  descr(phq.sum_score_prepan_raw, stats = "common")

glad.phq.raw.id %>%
  descr(phq.sum_score_prepan, stats = "common")
```

8 items
```{r phq prepan sum score if missigng items set to NA - all times}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_prepan =
      if_else(condition = na_per_person_phq_prepan > 1 &
                phq.missing_only_suicide_item_prepan == 1,
              true = NA_real_,
              false = phq.sum_score_prepan_raw,
              missing = NA_real_
      )
  )

glad.phq.raw.id %>%
  descr(phq.sum_score_8items_prepan_raw, stats = "common")

glad.phq.raw.id %>%
  descr(phq.sum_score_8items_prepan, stats = "common")
```
